Designing Robust Controllers With $H_{\infty}$ Performance Using Frequency-Domain Data

### 2017-02-14 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft/Draft.tex
updated files

\usepackage{graphicx}  % Add graphics capabilities
\usepackage{color}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}
%\usepackage{amsthm}
\usepackage{epstopdf}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\jo}{(j\omega)}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}

\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters} 
% Title, preferably not more than 10 words.

@@

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $T_\alpha \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$. The objective of this application is to design controllers such the TF from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G_d(s) &:= G_0(s)e^{-sT_\alpha}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k \in \{k_i,k_u,k_{m_1},k_{m_2}\}$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.  Then these closed-loop TF's can easily be derived as follows:

@@

{\bf Remark:} 
\textit{Note that the choice of the initializing gains in $k_0$ may affect the stability of the closed-loop system (for either the optimization problems concerning the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norms). The next section will discuss how to select these gains in order to ensure stability. \\ 
Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the gains in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}

@@

The following properties will be needed in order to properly analyze the stability conditions of the system:
\begin{definition}
Let wno$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, wno$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis). Then the following properties hold:
\begin{align}
\text{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \text{wno}\bigl\{ A_1(s) \bigr\} + \text{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
\text{wno}\bigl\{ A(s)\bigr\} &= -\text{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
\end{align}
\end{definition}

@@

\subsection{Controller Synthesis}
For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of $300 \: Hz$ and $500 \: Hz$ is attained, respectively (where both achieve a damping of $\zeta = 0.8$). Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d = T_d^*e^{-sT_\alpha}$ where $T_d^*$ was selected as a standard second order process, i.e.,
\begin{equation}
T_d^*(s) = \frac{\omega_d^2}{s^2 + 2\zeta \omega_d s + \omega_d^2}
\end{equation}
where $\zeta$ is the damping factor and
\begin{equation*}
\omega_d = \frac{2 \pi f_d}{\sqrt{1-2\zeta^2 + \sqrt{2-4\zeta^2 + 4\zeta^4}}}
\end{equation*}
where $f_d$ is the desired closed-loop bandwidth. In other words, $T_d$ is simply a delayed version of the second order process.

Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $T_\beta$ that was not captured in the identification experiment. This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$. The value of the delay is uncertain and is known to be in the range of $T_\beta \in [0,30]\mu s$. Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's. The grid was established in intervals of $5 \: \mu s$ (i.e., $T_{\beta_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).

In the $\mathcal{H}_{\infty}$ sense, the optimization problem to consider for this case study is as follows:
 \begin{equation} \label{eq:case_study_opt}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \|T_i(k)-T_d\|_{\infty}< \gamma \\
& &  &\|T_i^{\prime}(k)-T_d^{\prime}\|_{\infty}< \gamma \\ 
& & & i = 1,\ldots,7
\end{aligned}
\end{equation}
where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $T_{\beta_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$). A similar optimization problem can be considered for minimizing the $\mathcal{H}_2$ norm of the process. This optimization problem can be transformed to the convex problem by implementing the methods outlined in section \ref{sec:loop_shape}. 
\subsection{Experimental Results}
The constraints in the optimization problem in (\ref{eq:case_study_opt}) were first converted to LMI constraints; the problem was then converted to an SDP problem (since the transfer function analyzer provides the gain and phase at discrete frequency points). For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:loop_shape_LMI_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.

For comparative purposes, controllers were designed by considering the model of the process. There is uncertainty associated with the delay $T_\alpha$; the range of this uncertainty is $T_\alpha \in [0,200]\mu s$. Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) was solved by gridding in both $T_\alpha$ and $T_\beta$.

Fig.~\ref{fig:d_loop} shows the closed-loop frequency response of $|T^{\prime}(j\omega)|$ while Fig.~\ref{fig:v_loop} shows the closed-loop frequency response of $|T(j\omega)|$ for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process. From these figures, it can be observed that that model-based design produces the worst performance while the data-driven based design achieves the desired performance for both TF's. The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
\label{fig:d_loop}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_{\infty}$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
\label{fig:v_loop}
\end{figure}

>>>>

\usepackage{graphicx}  % Add graphics capabilities
\usepackage{color}
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{mathrsfs}

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

\usepackage{epstopdf}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{remark}{Remark}
\newtheorem{definition}{Definition}

\newcommand{\jo}{(j\omega)}
\newcommand{\jok}{(e^{-j\omega_k})}
\newcommand{\jro}{(e^{-j\omega},\rho)}
\newcommand{\jrok}{(e^{-j\omega_k},\rho)}

\title{A Data-Driven Loop-Shaping Approach to Design Controllers for Power Converters via Convex Optimization} 
% Title, preferably not more than 10 words.

@@

The system structure for this application is shown in Fig.~\ref{fig:damping_loop}. 
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/damping_loop_full}
\caption{Interconnection of the power converter control system. }
\label{fig:damping_loop}
\end{figure}
$G_0(s)$ represents the TF from $v_i$ to $v_0$ in Fig.~\ref{fig:circuit}; $H(s)$ represents the TF from $v_0$ to $i_c$; $P_1(s)$ and $P_2(s)$ are sensors (i.e., low-pass filters); $k_i$ and $k_u$ are the control variable gains; $\tau \: [s]$ is an actuation delay; and $C(s)$ is a PI controller (i.e., $C(s) = k_{p_1} + s^{-1}k_{p_2}$). From this framework, it can be observed that the inner feedback loops are reminiscent of a state-feedback control architecture while the system (as a whole) is a common unity feedback structure with feedforward action. For this application, note that $\{G_0,P_1,P_2 \} \in \mathscr{S}$ and $H \in \mathscr{P}$. The objective of this application is to design controllers such the TF from $v_d$ to $v_0$ and $v_r$ to $v_0$ both achieve the desired loop-shapes.

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(s,k) &:= k_iP_1(s)H(s);  &H_2(s,k) &:= k_uP_2(s) \\
G_d(s) &:= G_0(s)e^{-s\tau}; &C_m(s,k) &:= k_{m_1}+s^{-1}k_{m_2}\\ 
\end{aligned}
\end{equation}
where $k \in \{k_i,k_u,k_{m_1},k_{m_2}\}$. Let the TF from $v_d$ to $v_0$ be denoted as $T^{\prime}(s,k)$ and the TF from $v_r$ to $v_0$ be denoted as $T(s,k)$.  Then these closed-loop TF's can easily be derived as follows:

@@

\begin{remark}
\textit{Note that the choice of the initializing gains in $k_0$ may affect the stability of the closed-loop system (for either the optimization problems concerning the $\mathcal{H}_\infty$ or $\mathcal{H}_2$ norms). The next section will discuss how to select these gains in order to ensure stability. \\ 
Additionally, note that these optimization problems are considering the gains for $C_m(k)$; however, once an optimal solution is obtained for the gains in $k$, then the definitions in (\ref{eq:new_var}) can be used to revert back to the original gains (i.e., $k_{p_1}$ and $k_{p_2}$.)}
\end{remark}

@@

The following properties will be needed in order to properly analyze the stability conditions of the system:
\begin{definition}
Let \emph{wno}$\{ A(s)\}$ refer to the winding number; in the counterclockwise sense, \emph{wno}$\{ A(s)\}$ represents the image of $A(s)$ around the origin when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis). Then the following properties hold:
\begin{align}
\emph{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \emph{wno}\bigl\{ A_1(s) \bigr\} + \emph{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
\end{align}
\end{definition}

@@

\subsection{Controller Synthesis}
For this application, it was desired to shape $T^{\prime}(k)$ and $T(k)$ such that a bandwidth of $300 \: Hz$ and $500 \: Hz$ is attained, respectively (where both achieve a damping of $\zeta = 0.8$). Note that in both of these TF's, a pure delay appears in the numerator; therefore, the performance of the loop-shape algorithm can be improved by specifying a desired loop-shape $T_d(s) = T_d^*(s) e^{-s\tau}$ where $T_d^*(s)$ was selected as a standard second order process, i.e.,
\begin{equation}
T_d^*(s) = \frac{\omega_d^2}{s^2 + 2\zeta \omega_d s + \omega_d^2}
\end{equation}
where $\zeta$ is the damping factor and
\begin{equation*}
\omega_d = \frac{2 \pi f_d}{\sqrt{1-2\zeta^2 + \sqrt{2-4\zeta^2 + 4\zeta^4}}}
\end{equation*}
where $f_d$ is the desired closed-loop bandwidth. In other words, $T_d$ is simply a delayed version of the second order process. There is some uncertainty associated with the delay $\tau$; the range of this delay is $\tau \in [0,200]\mu s$ with a nominal value of $100 \mu s$. Therefore, for tracking purposes, $\tau = 100 \mu s$ in $T_d(s)$ can be selected as a viable performance criteria. Note that selecting $\tau$ to be another value within the uncertain range will not significantly impact the response. The critical values in the desired response are $f_d$ and $\zeta$.

Although the delay in $G_d$ was captured in the frequency response measurement, it is known that there also exists an additional measurement delay $\tau_e$ that was not captured in the identification experiment. This delay occurs after digitization of the analog signals at the outputs of $P_1$ and $P_2$. The value of the delay is uncertain and is known to be in the range of $\tau_e \in [0,30]\mu s$. Therefore, a multi-model design can be considered where the additional delay can be gridded in this range and incorporated into the closed-loop TF's. The grid was established in intervals of $5 \: \mu s$ (i.e., $\tau_{e_i} = [0,5,\ldots30] \mu s$, $i = 1,\ldots,7$).

In the $\mathcal{H}_{\infty}$ sense, the optimization problem to consider for this case study is as follows:
 \begin{equation} \label{eq:case_study_opt}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \|T_i(k)-T_d\|_{\infty}< \gamma \\
& &  &\|T_i^{\prime}(k)-T_d^{\prime}\|_{\infty}< \gamma \\ 
& & & i = 1,\ldots,7
\end{aligned}
\end{equation}
where $T_i(k)$ and $T_i^{\prime}(k)$ are the closed-loop TF's that incorporate the additional $i$-th delay in $\tau_{e_i}$; $T_d$ is the desired closed-loop TF for loop-shaping $T(k)$ (with a desired bandwidth of $f_d = 500 \: Hz$ and damping $\zeta = 0.8$); $T_d^{\prime}$ is the desired closed-loop TF for loop-shaping $T^{\prime}(k)$ (with a desired bandwidth of $f_d^{\prime} = 300 \: Hz$ and damping $\zeta^{\prime} = \zeta$). In the $\mathcal{H}_2$ sense, the optimization problem to consider is as follows:
\begin{equation} \label{eq:case_study_opt_2}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \int_0^{\infty} \gamma(\omega) d\omega  \\
& \text{subject to:} & & \|T_i(k)-T_d\|_2^2< \gamma(\omega) \\
& &  &\|T_i^{\prime}(k)-T_d^{\prime}\|_2^2< \gamma(\omega) \\ 
& & & i = 1,\ldots,7
\end{aligned}
\end{equation}
These optimization problems can be transformed to convex problems by implementing the methods outlined in section \ref{sec:loop_shape}. 
\subsection{Experimental Results}
The constraints in the optimization problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) were first converted to LMI constraints. Since the transfer function analyzer provides the gain and phase at discrete frequency points, the optimization problem then becomes an SDP problem. For solving the $\mathcal{H}_2$ problem in SDP form, the objective function in (\ref{eq:case_study_opt_2}) must be discretized where $\int \gamma(\omega) d\omega \rightarrow \sum_i \gamma(\omega_i)$.

For comparative purposes, controllers were designed by considering the model of the process.  Since there is uncertainty associated with the delay $\tau$, a multi-model approach can be implemented to ensure that the performance is attained for the uncertain values. Therefore, for the model-based design, the problem in (\ref{eq:case_study_opt}) and (\ref{eq:case_study_opt_2}) was solved by gridding in both $\tau$ and $\tau_e$.

Fig.~\ref{fig:d_loop} shows the closed-loop frequency response of $|T^{\prime}(j\omega)|$ while Fig.~\ref{fig:v_loop} shows the closed-loop frequency response of $|T(j\omega)|$ for the solutions obtained by minimizing both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ norms of the process. From these figures, it can be observed that that model-based design produces the worst performance while the data-driven based design achieves the desired performance for both TF's. The performance achieved by the data-driven method (in both the $\mathcal{H}_{\infty}$ and $\mathcal{H}_2$ minimization cases) are comparable.

\begin{remark}
Note that the solutions obtained for the model-based design were nearly identical for both the $\mathcal{H}_2$ and $\mathcal{H}_\infty$ problems. Hence the single result shown for the model-based design in Fig.~\ref{fig:d_loop} and Fig.~\ref{fig:v_loop}. 
\end{remark}

Table.~\ref{tab:case_study} displays the optimal solutions for all criteria considered in this case study.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/d_loop_mag.eps}
\caption{The closed-loop response of $|T^{\prime}(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $300 \: Hz$ bandwidth (dashed-black line).}
\label{fig:d_loop}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../pics/v_loop_mag.eps}
\caption{The closed-loop response of $|T(j\omega)|$; data-driven method with $\mathcal{H}_{\infty}$ performance (red line); data-driven method with $\mathcal{H}_2$ performance (blue line); model-based approach with $\mathcal{H}_2 / \mathcal{H}_\infty$ performance (yellow line); $-3 \: dB$ point representing $500 \: Hz$ bandwidth (dashed-black line).}
\label{fig:v_loop}
\end{figure}

\begin{table}[]
\centering
\caption{Comparison of optimal solutions between data-driven and model-based methodology}
\label{tab:case_study}
\begin{tabular}{c|c|c|c|c|c}
                                                                             & $k_i^*$ & $k_u^*$ & $k_{p_1}^*$ & $k_{p_2}^*$       & $\gamma^*$                                                     \\ \hline
\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$\\ (data-driven)\end{tabular} & $1.29$  & $3.80$  & $0.42$      & $2 \cdot 10^{-6}$ & $0.057$                                                        \\ \hline
\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_2$\\ (data-driven)\end{tabular}      & $1.39$  & $3.82$  & $0.60$      & $7 \cdot 10^{-7}$ & \begin{tabular}[c]{@{}c@{}}$0.108$\\ (peak value)\end{tabular} \\ \hline
\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_\infty$\\ (model-based)\end{tabular} & $0.95$  & $1.70$  & $0.48$      & $3 \cdot 10^{-7}$ & $0.149$                                                        \\ \hline
\begin{tabular}[c]{@{}c@{}}$\mathcal{H}_2$\\ (model-based)\end{tabular}      & $0.95$  & $1.70$  & $0.48$      & $3 \cdot 10^{-7}$ & \begin{tabular}[c]{@{}c@{}}$0.191$\\ (peak value)\end{tabular}
\end{tabular}
\end{table}

### 2017-02-14 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

\section{Conclusion} \label{sec:conclusion}
A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance. With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution with the order of the basis function $F$ approaches infinity. This solution is obtained by considering an optimization problem which guarantees the stability of the closed-loop system. The optimization problem is converted from an SIP problem to an SDP problem by gridding the frequency vector over a finite interval. The simulation examples show that the proposed approach achieves the optimal performance for a given controller order without any conservatism. For future work, it will be desired to implement this method for multi-input-multi-output (MIMO) systems and systems with controllers that possess multiple degrees-of-freedom.

>>>>

\section{Conclusion} \label{sec:conclusion}
A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance. With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution when the order of the basis function $F$ approaches infinity. This solution is obtained by considering an optimization problem which guarantees the stability of the closed-loop system. The optimization problem is converted from an SIP problem to an SDP problem by gridding the frequency vector over a finite interval. The simulation examples show that the proposed approach achieves the optimal performance for a given controller order without any conservatism. For future work, it will be desired to implement this method for multi-input-multi-output (MIMO) systems and systems with controllers that possess multiple degrees-of-freedom.
